### 2015-04-01 paper.tex
Craeted skeleton for our final paper

\documentclass{article}

\author{Jonathan Brandt, Skyler Manzanares, William Fong}
\date{April 2, 2015}
\title{Programming Assignment 2}

\maketitle

%I don't know what sections we need! Add and remove as you see fit
\section{Overview}

\section{Program Description}

\section{Member Assignments}

### 2015-04-01 hamming.m
Renamed vectorization to hamming

@@ -1,12 +1,74 @@
-function output=hamming(InputVector, WeightMatrix)
-i=0;
-[w,h] = size(WeightMatrix)
+function output=hamming(input)
+    
 
-output= zeros(1,w)
+    if (~isdir(input))
+        %assume its a single file name
+        fprintf('Processing file: %s\n', input);
+        img = polarize(input);
+        output = img(:);
+        output = output';
+        return;
+    else
+        olddir = pwd;
+        cd(input);
+    
+        files = dir('*.jpg');
+        
+        %init empty matrix
+        output = zeros(307200, length(files));
+        for i=1:length(files)
+            filename = files(i).name;
+            fprintf('Processing file: %s\n', filename);
+            
+            %polarize the image
+            img = polarize(filename);
+            
+             %get image as a 1 x n vector
+            vect = img(:);
 
-for i= 1:w
-    b=InputVector;
-    a=WeightMatrix(i,:);
-    hammingDist = @(a,b)sum( a(:)~= b(:));
-    output(i)= hammingDist(a,b);
+            %transpose so it's a column vector
+            vect = vect';
+
+            %set the i'th COL to be the same as our vector
+            output(:,i) = vect;
+            i = i + 1;
+            
+        end
+    end
+    
+    %return to the old directory
+    cd(olddir);
+
+end
+
+function output=polarize(img)
+    if (ischar(img))
+       img = getImage(img);
+    end
+    
+    img = resizeImage(img);
+    
+    output = rgb2gray(img);
+    output = threshhold(output);
+end
+
+function img=getImage(filename)
+    img = imread(filename);
+end
+
+function img=resizeImage(imgIn)
+    img=imresize(imgIn, [480, 640]);
+end
+
+function output=threshhold(InputMatrix)
+    [w,h,d] = size(InputMatrix);
+    for i=1:w
+    for j=1:h
+       if (InputMatrix(i,j) < 128)
+          output(i,j) = 0;
+       else
+           output(i,j) = 1;
+       end
+    end
+    end
 end

### 2015-04-01 vectorization.m

@@ -1,74 +1,0 @@
-function output=vectorization(input)
-    
-
-    if (~isdir(input))
-        %assume its a single file name
-        fprintf('Processing file: %s\n', input);
-        img = polarize(input);
-        output = img(:);
-        output = output';
-        return;
-    else
-        olddir = pwd;
-        cd(input);
-    
-        files = dir('*.jpg');
-        
-        %init empty matrix
-        output = zeros(307200, length(files));
-        for i=1:length(files)
-            filename = files(i).name;
-            fprintf('Processing file: %s\n', filename);
-            
-            %polarize the image
-            img = polarize(filename);
-            
-             %get image as a 1 x n vector
-            vect = img(:);
-
-            %transpose so it's a column vector
-            vect = vect';
-
-            %set the i'th COL to be the same as our vector
-            output(:,i) = vect;
-            i = i + 1;
-            
-        end
-    end
-    
-    %return to the old directory
-    cd(olddir);
-
-end
-
-function output=polarize(img)
-    if (ischar(img))
-       img = getImage(img);
-    end
-    
-    img = resizeImage(img);
-    
-    output = rgb2gray(img);
-    output = threshhold(output);
-end
-
-function img=getImage(filename)
-    img = imread(filename);
-end
-
-function img=resizeImage(imgIn)
-    img=imresize(imgIn, [480, 640]);
-end
-
-function output=threshhold(InputMatrix)
-    [w,h,d] = size(InputMatrix);
-    for i=1:w
-    for j=1:h
-       if (InputMatrix(i,j) < 128)
-          output(i,j) = 0;
-       else
-           output(i,j) = 1;
-       end
-    end
-    end
-end

### 2015-04-01 hamming.m
Update output of hamming weight matrix creation to be bipolar instead of binary

@@ -65,7 +65,7 @@ function output=threshhold(InputMatrix)
     for i=1:w
     for j=1:h
        if (InputMatrix(i,j) < 128)
-          output(i,j) = 0;
+          output(i,j) = -1;
        else
            output(i,j) = 1;
        end

### 2015-04-01 bam.m
Fleshed out creation of bam matrix

@@ -1,0 +1,16 @@
+%Expects a matrix with each COLUMN being a centroid
+function output=bam(inputmatrix)
+    [w,h] = size(inputmatrix(:, 1));
+    output = zeros(h, h);
+    
+    for i=1:w
+       output = output + getWeight(inputmatrix(:, i));
+    end
+    
+    
+end
+
+function weightMatrix = getWeight(inputVector)
+   transVect = inputVector';
+   weightMatrix = transVect * inputVector;
+end

### 2015-04-01 ham.m
Accurately call the file ham, not bam

@@ -1,5 +1,5 @@
 %Expects a matrix with each COLUMN being a centroid
-function output=bam(inputmatrix)
+function output=ham(inputmatrix)
     [w,h] = size(inputmatrix(:, 1));
     output = zeros(h, h);
     

### 2015-04-01 HammingMax.m
Recreated Jon's hammingM and renamed my hamming.m HammingMax.m

@@ -1,0 +1,74 @@
+function output=hamming(input)
+    
+
+    if (~isdir(input))
+        %assume its a single file name
+        fprintf('Processing file: %s\n', input);
+        img = polarize(input);
+        output = img(:);
+        output = output';
+        return;
+    else
+        olddir = pwd;
+        cd(input);
+    
+        files = dir('*.jpg');
+        
+        %init empty matrix
+        output = zeros(307200, length(files));
+        for i=1:length(files)
+            filename = files(i).name;
+            fprintf('Processing file: %s\n', filename);
+            
+            %polarize the image
+            img = polarize(filename);
+            
+             %get image as a 1 x n vector
+            vect = img(:);
+
+            %transpose so it's a column vector
+            vect = vect';
+
+            %set the i'th COL to be the same as our vector
+            output(:,i) = vect;
+            i = i + 1;
+            
+        end
+    end
+    
+    %return to the old directory
+    cd(olddir);
+
+end
+
+function output=polarize(img)
+    if (ischar(img))
+       img = getImage(img);
+    end
+    
+    img = resizeImage(img);
+    
+    output = rgb2gray(img);
+    output = threshhold(output);
+end
+
+function img=getImage(filename)
+    img = imread(filename);
+end
+
+function img=resizeImage(imgIn)
+    img=imresize(imgIn, [480, 640]);
+end
+
+function output=threshhold(InputMatrix)
+    [w,h,d] = size(InputMatrix);
+    for i=1:w
+    for j=1:h
+       if (InputMatrix(i,j) < 128)
+          output(i,j) = -1;
+       else
+           output(i,j) = 1;
+       end
+    end
+    end
+end

### 2015-04-01 hamming.m

@@ -1,74 +1,10 @@
-function output=hamming(input)
-    
-
-    if (~isdir(input))
-        %assume its a single file name
-        fprintf('Processing file: %s\n', input);
-        img = polarize(input);
-        output = img(:);
-        output = output';
-        return;
-    else
-        olddir = pwd;
-        cd(input);
-    
-        files = dir('*.jpg');
-        
-        %init empty matrix
-        output = zeros(307200, length(files));
-        for i=1:length(files)
-            filename = files(i).name;
-            fprintf('Processing file: %s\n', filename);
-            
-            %polarize the image
-            img = polarize(filename);
-            
-             %get image as a 1 x n vector
-            vect = img(:);
-
-            %transpose so it's a column vector
-            vect = vect';
-
-            %set the i'th COL to be the same as our vector
-            output(:,i) = vect;
-            i = i + 1;
-            
-        end
-    end
-    
-    %return to the old directory
-    cd(olddir);
-
-end
-
-function output=polarize(img)
-    if (ischar(img))
-       img = getImage(img);
-    end
-    
-    img = resizeImage(img);
-    
-    output = rgb2gray(img);
-    output = threshhold(output);
-end
-
-function img=getImage(filename)
-    img = imread(filename);
-end
-
-function img=resizeImage(imgIn)
-    img=imresize(imgIn, [480, 640]);
-end
-
-function output=threshhold(InputMatrix)
-    [w,h,d] = size(InputMatrix);
-    for i=1:w
-    for j=1:h
-       if (InputMatrix(i,j) < 128)
-          output(i,j) = -1;
-       else
-           output(i,j) = 1;
-       end
-    end
-    end
+function output=hamming(InputVector, WeightMatrix)
+i=0;
+[w,h] = size(WeightMatrix)
+output= zeros(1,w)
+for i= 1:w
+b=InputVector;
+a=WeightMatrix(i,:);
+hammingDist = @(a,b)sum( a(:)~= b(:));
+output(i)= hammingDist(a,b);
 end

### 2015-04-01 bam.m
Working hard to get the proper output weight matrix for a bam

@@ -1,0 +1,21 @@
+%Expects a matrix with each COLUMN being a centroid
+function output=ham(inputmatrix)
+    [h,w] = size(inputmatrix);
+    output = zeros(h, h);
+    
+    for i=1:w
+       output = output + getWeight(inputmatrix(:, i))
+    end
+    
+    %go through and zero out the diagonal
+    for i=1:h
+       output(i,i) = 0;
+    end
+    
+    
+end
+
+function weightMatrix = getWeight(inputVector)
+   transVect = inputVector';
+   weightMatrix = inputVector * transVect;
+end

### 2015-04-01 bam.m
Added implementation for the BAM network. Debugging still required

@@ -1,0 +1,15 @@
+%This Function operates correctly when the input_vector is horizontal
+%and the centroid_vector is vertical in structure.
+function output_vector = bam( input_vector, centroid_vector )
+%This function applies a Bidirectional Associative Memory
+%Algorithm against 2 input vectors
+
+%Determined transposed weight
+centroid_trans = centroid_vector';
+%Find the Y neuron layer output
+Y_layer_output = centroid_vector * input_vector;
+%Put the Y output back into a transposed weight vector
+%This is to get back out stored output
+output_vector = Y_layer_output * centroid_trans;
+end
+

### 2015-04-01 bam.m
Fixed slip-up with overwriting bam

@@ -1,21 +1,15 @@
-%Expects a matrix with each COLUMN being a centroid
-function output=ham(inputmatrix)
-    [h,w] = size(inputmatrix);
-    output = zeros(h, h);
-    
-    for i=1:w
-       output = output + getWeight(inputmatrix(:, i))
-    end
-    
-    %go through and zero out the diagonal
-    for i=1:h
-       output(i,i) = 0;
-    end
-    
-    
+%This Function operates correctly when the input_vector is horizontal
+%and the centroid_vector is vertical in structure.
+function output_vector = bam( input_vector, centroid_vector )
+%This function applies a Bidirectional Associative Memory
+%Algorithm against 2 input vectors
+
+%Determined transposed weight
+centroid_trans = centroid_vector';
+%Find the Y neuron layer output
+Y_layer_output = centroid_vector * input_vector;
+%Put the Y output back into a transposed weight vector
+%This is to get back out stored output
+output_vector = Y_layer_output * centroid_trans;
 end
 
-function weightMatrix = getWeight(inputVector)
-   transVect = inputVector';
-   weightMatrix = inputVector * transVect;
-end

### 2015-04-01 ham.m

@@ -1,10 +1,15 @@
 %Expects a matrix with each COLUMN being a centroid
 function output=ham(inputmatrix)
-    [w,h] = size(inputmatrix(:, 1));
+    [h,w] = size(inputmatrix);
     output = zeros(h, h);
     
     for i=1:w
-       output = output + getWeight(inputmatrix(:, i));
+       output = output + getWeight(inputmatrix(:, i))
+    end
+    
+    %go through and zero out the diagonal
+    for i=1:h
+       output(i,i) = 0;
     end
     
     
@@ -12,5 +17,5 @@ end
 
 function weightMatrix = getWeight(inputVector)
    transVect = inputVector';
-   weightMatrix = transVect * inputVector;
+   weightMatrix = inputVector * transVect;
 end

### 2015-04-01 bam.m
Added further implementation of the BAM network

@@ -1,13 +1,14 @@
 %This Function operates correctly when the input_vector is horizontal
-%and the centroid_vector is vertical in structure.
-function output_vector = bam( input_vector, centroid_vector )
-%This function applies a Bidirectional Associative Memory
-%Algorithm against 2 input vectors
-
-%Determined transposed weight
-centroid_trans = centroid_vector';
-%Find the Y neuron layer output
-Y_layer_output = centroid_vector * input_vector;
-%Put the Y output back into a transposed weight vector
-%This is to get back out stored output
-output_vector = Y_layer_output * centroid_trans;
+%and the centroid_matrix is arranged vertically.
+function output_matrix = bam( input_vector, centroid_matrix )
+    %This function applies a Bidirectional Associative Memory
+    %Algorithm
+    WeightMatrix;
+    [columns, rows] = size(bam);
+    %Find weights per matrix and find sum
+    for col=1:columns
+        tmpMatrix = col * input_vector;
+        WeightMatrix += tmpMatrix;
+    end
+    
+    output_matrix = WeightMatrix;

### 2015-04-01 ham.m
Finished up creating the weight matrix of a HAM network

@@ -12,7 +12,6 @@ function output=ham(inputmatrix)
        output(i,i) = 0;
     end
     
-    
 end
 
 function weightMatrix = getWeight(inputVector)

### 2015-04-01 Weight.m
Added function weight.m to avg the img's for a weight prototype.  modified hamming.m for stuff, reorganized the img files for usability o Please enter the commit message for your changes. Lines starting

@@ -1,0 +1,69 @@
+function output=Weight(input)
+
+    if (~isdir(input))
+        %assume its a single file name
+        fprintf('Processing file: %s\n', str(input));
+        img = polarize(input);
+        output = img;
+        return;
+    else
+        olddir = pwd;
+        cd(input);
+    
+        files = dir('*.jpg');
+        
+        %init empty matrix
+        output = zeros(48, 64);
+        for i=1:length(files)
+            filename = files(i).name;
+            fprintf('Processing file: %s\n', filename);
+            
+            %polarize the image
+            img = polarize(filename);
+            %img matrix is added to output matrix
+            output= output + img;
+            i=i+1;
+        end
+    end
+    
+    %all img matrices should be added, now averaged
+   output= output/i;
+   output=output*148;  %skews values for proper threshhold
+   output= threshhold(output); %threshhold the avg
+   %output= (2*output) - 1;
+   
+    
+end
+    
+    
+    function output=polarize(img)
+    if (ischar(img))
+       img = getImage(img);
+    end
+    
+    img = resizeImage(img);
+    
+    output = rgb2gray(img);
+    output = threshhold(output);
+end
+
+function img=getImage(filename)
+    img = imread(filename);
+end
+
+function img=resizeImage(imgIn)
+    img=imresize(imgIn, [48, 64]);
+end
+
+function output=threshhold(InputMatrix)
+    [w,h,d] = size(InputMatrix);
+    for i=1:w
+    for j=1:h
+       if (InputMatrix(i,j) < 128)
+          output(i,j) = 0;
+       else
+           output(i,j) = 1;
+       end
+    end
+    end
+end

### 2015-04-01 hamming.m

@@ -1,12 +1,16 @@
 function output=hamming(InputVector, WeightMatrix)
 i=0;
+%get dimensions of the weightmatrix
 [w,h] = size(WeightMatrix)
-
+%allocate output array to store hamming dist
 output= zeros(1,w)
 
+%iterates through each column vector of weightmatrix, computes hamming
+%distance between inputvector and iteration's vector
 for i= 1:w
     b=InputVector;
     a=WeightMatrix(i,:);
     hammingDist = @(a,b)sum( a(:)~= b(:));
+    %stores hammingdist in output
     output(i)= hammingDist(a,b);
 end

### 2015-04-01 ham.m
Added some comments detailing the logic

@@ -1,4 +1,5 @@
 %Expects a matrix with each COLUMN being a centroid
+%
 function output=ham(inputmatrix)
     [h,w] = size(inputmatrix);
     output = zeros(h, h);

### 2015-04-01 paper.tex
Added sections and subsections as per Project Report specs

@@
 
-%I don't know what sections we need! Add and remove as you see fit
+%Feel free to remove the 'description' text i placed (e.g. "Our hopfield network was terrific! Type stuff here")
 \section{Overview}
 
-\section{Program Description}
+\section{Hopfield Autoassociative Memory Network}
+Our hopfield network was terrific! Type stuff here
+
+\subsection{Image Encoding}
+The image encoding... blah blah. Type here
+
+\subsection{Performance}
+Here is where we need to talk about how long it took and how good it was. We
+also might want to mention the size limitations this introduced!
+
+\subsection{Sensitivity}
+This section is about how badly noise and the size disrupted our accuracy
+
+\subsection{Comments}
+It says "your own observation and conclusions about the experiment."
+I'm thinking we talk generally about how it did (like a conclusion) and how
+what we did ended up working.
+
+\section{Hamming-Max Network}
+
+\subsection{Image Encoding}
+The image encoding... blah blah. Type here
+
+\subsection{Performance}
+Here is where we need to talk about how long it took and how good it was. We
+also might want to mention the size limitations this introduced!
+
+\subsection{Sensitivity}
+This section is about how badly noise and the size disrupted our accuracy
+
+\subsection{Comments}
+It says "your own observation and conclusions about the experiment."
+I'm thinking we talk generally about how it did (like a conclusion) and how
+what we did ended up working.
+
+\section{Bidirection Associative Memory (BAM)}
+
+\subsection{Image Encoding}
+The image encoding... blah blah. Type here
+
+\subsection{Performance}
+Here is where we need to talk about how long it took and how good it was. We
+also might want to mention the size limitations this introduced!
+
+\subsection{Sensitivity}
+This section is about how badly noise and the size disrupted our accuracy
+
+\subsection{Comments}
+It says "your own observation and conclusions about the experiment."
+I'm thinking we talk generally about how it did (like a conclusion) and how
+what we did ended up working.
+
+\section{LVQ}
+
+\subsection{Image Encoding}
+The image encoding... blah blah. Type here
+
+\subsection{Performance}
+Here is where we need to talk about how long it took and how good it was. We
+also might want to mention the size limitations this introduced!
+
+\subsection{Sensitivity}
+This section is about how badly noise and the size disrupted our accuracy
+
+\subsection{Comments}
+It says "your own observation and conclusions about the experiment."
+I'm thinking we talk generally about how it did (like a conclusion) and how
+what we did ended up working.
 

### 2015-04-01 Weight.m
Added return CD back to olddir

@@ -32,7 +32,7 @@ function output=Weight(input)
    output= threshhold(output); %threshhold the avg
    %output= (2*output) - 1;
    
-    
+   cd(olddir); 
 end
     
     

### 2015-04-01 paper.tex
Included \begin{document} as required
Defined the Member Assignment section

@@
 \documentclass{article}
+\begin{document}
 
@@
 \section{Member Assignments}
+All members were involved in some manner in all major area of the project. These
+major areas include the paper writup, the presentation creation, and the 
+programming. The specific assignements per group member are given below, but no
+single member handled an entire area of development.
+\subsection{Jonathan Brandt}
+\subsubsection{Programming}
+Jonathan's programming work was divided between implementation of the 
+Hamming/Max network and the creation of centroids for the networks based on a
+large number of sample inputs. He was completely responsible for creating the Hamming layer of the Hamming/MAX network, and worked in conjunction with the rest of the team when creating the centroids.
+
+\subsubsection{Project Report}
+Jonathan was tasked with the Hamming/Max section? or perhaps the LVQ
+
+\subsubsection{Project Presentation}
+NOTHING HE DID NOTHING 0 percent FOR HIM
+
+\subsection{Skyler Manzanares}
+\subsubsection{Programming}
+Skyler implemented the formatting of centroid images to the weight matrix to be fed into the Hamming/MAX network.
+He also did extensive work creating the functions that read in and format images.
+Skyler was also responsible for implementing
+the HAM network.
+
+\subsubsection{Project Report}
+Skyler created the template for the project report and was in charge of the HAM 
+network section and the Member Assignment section.
+
+\subsubsection{Project Presentation}
+lulz he ain't done a thing.
+
+\subsection{William Fong}
+\subsubsection{Programming}
+William worked to creat the Max layer of the Hamming/Max network and coordinate 
+inputs and outputs of the various layers, summing all components together to create a working Hamming/Max network. William was also in charge of implementing the BAM network.
+
+\subsubsection{Project Report}
+William was tasked to the BAM section.
+
+\subsubsection{Project Presentation}
+nuthin.
+
+\end{document}

### 2015-04-01 Weight.m
Did a lot of balancing on average function to use the square of the new image totry and get a more accurate centroid -- accounting for gray creating through resizing

@@ -13,7 +13,7 @@ function output=Weight(input)
         files = dir('*.jpg');
         
         %init empty matrix
-        output = zeros(48, 64);
+        output = zeros(48, 64)
         for i=1:length(files)
             filename = files(i).name;
             fprintf('Processing file: %s\n', filename);
@@ -21,30 +21,29 @@ function output=Weight(input)
             %polarize the image
             img = polarize(filename);
             %img matrix is added to output matrix
-            output= output + img;
-            i=i+1;
+            output= (img .* img) + output;
+            %i=i+1;
         end
     end
-    
     %all img matrices should be added, now averaged
    output= output/i;
    output=output*148;  %skews values for proper threshhold
-   output= threshhold(output); %threshhold the avg
+   output= threshhold(output, 127); %threshhold the avg
    %output= (2*output) - 1;
    
    cd(olddir); 
 end
     
     
-    function output=polarize(img)
+function output=polarize(img)
     if (ischar(img))
        img = getImage(img);
     end
     
     img = resizeImage(img);
     
-    output = rgb2gray(img);
-    output = threshhold(output);
+    img = rgb2gray(img);
+    output = threshhold(img, 230);
 end
 
 function img=getImage(filename)
@@ -52,14 +51,15 @@ function img=getImage(filename)
 end
 
 function img=resizeImage(imgIn)
-    img=imresize(imgIn, [48, 64]);
+    img=imresize(imgIn, [48, 64], 'bilinear');
+    %img = imresize(imgIn, [48, 64]);
 end
 
-function output=threshhold(InputMatrix)
+function output=threshhold(InputMatrix, thresh)
     [w,h,d] = size(InputMatrix);
     for i=1:w
     for j=1:h
-       if (InputMatrix(i,j) < 128)
+       if (InputMatrix(i,j) < thresh)
           output(i,j) = 0;
        else
            output(i,j) = 1;

### 2015-04-01 Weight.m
Removed a bunch of spam and pauses that were for testing

@@ -2,9 +2,9 @@ function output=Weight(input)
 
     if (~isdir(input))
         %assume its a single file name
-        fprintf('Processing file: %s\n', str(input));
+        fprintf('Processing file: %s\n', input);
         img = polarize(input);
-        output = img;
+        output = img(:);
         return;
     else
         olddir = pwd;
@@ -13,15 +13,16 @@ function output=Weight(input)
         files = dir('*.jpg');
         
         %init empty matrix
-        output = zeros(48, 64)
+        output = zeros(3072, 1)
         for i=1:length(files)
             filename = files(i).name;
             fprintf('Processing file: %s\n', filename);
             
             %polarize the image
             img = polarize(filename);
+            vect = img(:);
             %img matrix is added to output matrix
-            output= (img .* img) + output;
+            output= (vect .* vect) + output;
             %i=i+1;
         end
     end
@@ -29,8 +30,9 @@ function output=Weight(input)
    output= output/i;
    output=output*148;  %skews values for proper threshhold
    output= threshhold(output, 127); %threshhold the avg
-   %output= (2*output) - 1;
+   output= (2*output) - 1;
    
+   %output = output(:);
    cd(olddir); 
 end
     

### 2015-04-01 ham.m

@@ -5,7 +5,7 @@ function output=ham(inputmatrix)
     output = zeros(h, h);
     
     for i=1:w
-       output = output + getWeight(inputmatrix(:, i))
+       output = output + getWeight(inputmatrix(:, i));
     end
     
     %go through and zero out the diagonal

### 2015-04-01 HamNet.m
Constructed HamNet, which incorporates all parts of creating the HAM network and classifying input.

@@ -1,0 +1,72 @@
+%Constructs a ham network based on the passed centroids and then
+%tries to classify the passed input vector. 
+%HamNet(centroidMatrix, inputVector)
+%centroidMatrix - Matrix of centroids. Each COL is a centroid
+%inputVector - Vector to classify. this should be a single Column
+%delta - how small the average distance between the current and last
+%       iteration should be before considering the system converged.
+%       numbers are from 0 to 1, so a delta of .01 to .1 is best
+%This function takes the classification and then uses a HAMMING MAX
+%to figure out which centroid it's closest to and returns that instead of
+%the raw classification vector.
+function output = HamNet(centroidMatrix, inputVector, delta)
+    weightMatrix = ham(centroidMatrix);
+    
+    [h, w, d] = size(weightMatrix);
+    
+    fprintf('Starting HAM classification!\n');
+    
+    d = 1;
+    sens = 25;
+    index = 1;
+    oldIn = inputVector;
+    while (d > delta)
+       %to avoid seeming-deadlock, we report that the program is still
+       %iterating. To avoid spamming, we increase iterations between
+       %reports by doubling the distance
+       if (index == sens)
+          fprintf('Beginning iteration %d. Previous Delta: %d\n', index, d);
+          sens = sens * 2;
+       end
+       
+       %fetch the current iteration's classification
+       classification = weightMatrix * oldIn;
+       
+       %apply theshhold function to classification
+       classification = threshhold(classification);
+       
+       %find average absolute distance between iterations
+       d = 0;
+       for i=1:h
+            %sum all differences up
+            d = d + (abs(oldIn(i, 1) - classification(i, 1)));
+       end
+       d = d / h;
+       index = index + 1;
+       oldIn = classification;
+    end
+    
+    %we have the finished vector classification. Now which is it closest
+    %to?
+    %We use a hamming function here even though it's not conventionally
+    %part of the network because this is soft computing and classification
+    %can be iffy
+    hammingVect = hamming(oldIn', centroidMatrix);
+    
+    hammingIndex = maxNet(hammingVect);
+    
+    output = centroidMatrix(:, hammingIndex);
+end
+
+function output=threshhold(InputMatrix)
+    [w,h,d] = size(InputMatrix);
+    for i=1:w
+    for j=1:h
+       if (InputMatrix(i,j) < 0)
+          output(i,j) = 0;
+       else
+           output(i,j) = 1;
+       end
+    end
+    end
+end

### 2015-04-01 HammingMax.m

@@ -1,4 +1,4 @@
-function output=hamming(input)
+function output=HammingMax(input)
     
 
     if (~isdir(input))

### 2015-04-01 hamming.m

@@ -3,13 +3,13 @@ i=0;
 %get dimensions of the weightmatrix
 [w,h] = size(WeightMatrix)
 %allocate output array to store hamming dist
-output= zeros(1,w)
+output= zeros(1,h);
 
 %iterates through each column vector of weightmatrix, computes hamming
 %distance between inputvector and iteration's vector
-for i= 1:w
+for i= 1:h
     b=InputVector;
-    a=WeightMatrix(i,:);
+    a=WeightMatrix(:, i);
     hammingDist = @(a,b)sum( a(:)~= b(:));
     %stores hammingdist in output
     output(i)= hammingDist(a,b);

### 2015-04-01 bam.m
Noticed that the BAM implementation accidentally called itself. This is now corrected.

@@ -4,7 +4,7 @@ function output_matrix = bam( input_vector, centroid_matrix )
     %This function applies a Bidirectional Associative Memory
     %Algorithm
     WeightMatrix;
-    [columns, rows] = size(bam);
+    [columns, rows] = size(centroid_matrix);
     %Find weights per matrix and find sum
     for col=1:columns
         tmpMatrix = col * input_vector;

### 2015-04-02 paper.tex
Update paper.tex
Added content to the HAMMING/MAX section

@@
 \section{Hamming-Max Network}
+The Hamming-Max was fairly straight forward to construct.
+We first created the hammingnet portion which was given the input vector and weight matrix.
+It computed the hamming distance of the input from each column vector prototype of the weight matrix, storing those values in an output vector, equal in width to the weight matrix.
+We then constructed the Maxnet which was given the Hammingnet output as a parameter.
+It subtracts 1 from each element until a single zero value is found, declaring it the smallest hamming distance.
+This index represents the prototype which is most similar to the input, suggesting the input must be of this classification.
 
 \subsection{Image Encoding}
-The image encoding... blah blah. Type here
+Deciding how to encode our images was a bit tricky.
+We played with a few different ways of obtaining image outlines however, we decided for this network, simply finding images already in outline form would be best.
+We removed inner detail from these outlines and ran them through a program we wrote.
+First, the images are resized so that they are all one standard size,  the images are then grayscaled and run through a threshhold function so that a clear outline of black on white is present.
+To establish the prototypes for our weight matrix, we added the values of each representative image matrix to eachother, then averaged the values and processed the result as before.
+We adjusted our threshhold function to maintain clarity.
+We found that visually, too small a size diminshed image definition, while too large was time and resource intensive and lacked definitive shape for the prototype matrix.
 
@@
 \subsubsection{Project Report}
-Jonathan was tasked with the Hamming/Max section? or perhaps the LVQ
+Jonathan was tasked with the Hamming/Max section.
 
 \subsubsection{Project Presentation}
-NOTHING HE DID NOTHING 0 percent FOR HIM
+NOTHING HE DID NOTHING 0 percent FOR HIM....DAMN YOU SKYLER
 
-\subsection{Skyler Manzanares}
+\subsection{Skyler "Scrub" Manzanares}
 \subsubsection{Programming}
@@
 \subsubsection{Project Presentation}
-lulz he ain't done a thing.
+lulz he ain't done a thing.  0\% for you
 
@@
 \subsubsection{Project Presentation}
-nuthin.
+nuthin. no soup for you
 

### 2015-04-02 bam.m
Added further implementation of BAM

@@ -1,5 +1,6 @@
-%This Function operates correctly when the input_vector is horizontal
+%   This Function operates correctly when the input_vector is horizontal
 %and the centroid_matrix is arranged vertically.
+%   This function will return the created weight matrix;
 function output_matrix = bam( input_vector, centroid_matrix )
     %This function applies a Bidirectional Associative Memory
     %Algorithm
@@ -14,9 +15,18 @@ function output_matrix = bam( input_vector, centroid_matrix )
     output_matrix = WeightMatrix;
 end
 
-%This function operates correctly when the input_vector is horizontal
+%   This function operates correctly when the input_vector is horizontal
 %and the centroid_matrix is arranged vertically
-function output_matrix = bam( input_vector, centroid_matrix)
+%   This function will return the TRANSPOSED weight matrix.
+function output_matrix = bam_transposed( input_vector, centroid_matrix)
     WeightMatrix;
-    []
+    centroid_matrix = centroid_matrix';
+    [columns, rows] = size(centroid_matrix);
+    %Find weights per matrix and find sum
+    for col=1:columns
+       tmpMatrix = centroidMatrix(:,col) * input_vector;
+       WeightMatrix = WeightMatrix + tmpMatrix;
+    end
+    %Return the created Weight Matrix
+    output_matrix = WeightMatrix;
 end

### 2015-04-02 HamNet.m
Spit out how many iterations the HAM worked in when it finishes

@@ -56,6 +56,7 @@ function output = HamNet(centroidMatrix, inputVector, delta)
     hammingIndex = maxNet(hammingVect);
     
     output = centroidMatrix(:, hammingIndex);
+    fprintf('Converged in %d iterations.\n', index);
 end
 
 function output=threshhold(InputMatrix)

### 2015-04-02 HamNet.m
doing what skyler tells me

@@ -51,7 +51,8 @@ function output = HamNet(centroidMatrix, inputVector, delta)
     %We use a hamming function here even though it's not conventionally
     %part of the network because this is soft computing and classification
     %can be iffy
-    hammingVect = hamming(oldIn', centroidMatrix);
+    hammingVect = hamming(oldIn', centroidMatrix)
+    pause;
     
     hammingIndex = maxNet(hammingVect);
     

### 2015-04-02 Weight.m

@@ -5,6 +5,7 @@ function output=Weight(input)
         fprintf('Processing file: %s\n', input);
         img = polarize(input);
         output = img(:);
+        output= -((2*output) - 1);
         return;
     else
         olddir = pwd;
@@ -30,7 +31,7 @@ function output=Weight(input)
    output= output/i;
    output=output*148;  %skews values for proper threshhold
    output= threshhold(output, 127); %threshhold the avg
-   output= (2*output) - 1;
+   output= -((2*output) - 1);
    
    %output = output(:);
    cd(olddir); 

### 2015-04-02 paper.tex
Corrected BAM implementation.

@@
 
-\subsection{Skyler "Scrub" Manzanares}
+\subsection{Skyler "Scrub on the Frub" Manzanares}
 \subsubsection{Programming}
@@
 \subsubsection{Programming}
-William worked to creat the Max layer of the Hamming/Max network and coordinate 
+William worked to create the Max layer of the Hamming/Max network and coordinate 
 inputs and outputs of the various layers, summing all components together to create a working Hamming/Max network. William was also in charge of implementing the BAM network.

### 2015-04-02 HammingMax.m
I don't remember what i did. Also i created a LVQ network creation function

@@ -15,7 +15,7 @@ function output=HammingMax(input)
         files = dir('*.jpg');
         
         %init empty matrix
-        output = zeros(307200, length(files));
+        output = zeros(3072, length(files));
         for i=1:length(files)
             filename = files(i).name;
             fprintf('Processing file: %s\n', filename);
@@ -57,7 +57,7 @@ function img=getImage(filename)
 end
 
 function img=resizeImage(imgIn)
-    img=imresize(imgIn, [480, 640]);
+    img=imresize(imgIn, [48, 64]);
 end
 
 function output=threshhold(InputMatrix)

### 2015-04-02 bam.m
Added some testing tools for BAM

@@ -14,18 +14,18 @@ end
 %classification Vector by our Weight Matrix. In otherwords, we enter
 %"Giraffe" and this Matrix will return what it thinks a Giraffe is.
 %bamT(input_vector, centroid_matrix, class_matrix)
-%input_vector - This is the classification vector.
+%class_vector - This is the classification vector.
 %centroid_matrix - This is the cntroid matrix containing all of the defined
 %               crentoids. Each individual centroid must be aligned
 %               verticaly in order for this function to return properly.
 %class_matrix - This matrix stores all of our classificiations (e.g. what
 %               the input is to be associated with). These classifications
 %               MUST be aligned horizontally!
-function output_vector = bamT( input_vector, centroid_matrix, class_matrix)
+function output_vector = bamT( class_vector, centroid_matrix, class_matrix)
     %This is the Y layer of neurons
     WeightMatrix = bam_weight_T(class_matrix, centroid_matrix);
     %X_association is what BAM associates with a classification.
-    X_association = input_vector * WeightMatrix;
+    X_association = class_vector * WeightMatrix;
     output_vector = X_association.
 end
 
@@ -76,4 +76,9 @@ function output_matrix = bam_weight_T( input_vector, class_matrix)
     end
     %Return the created Weight Matrix
     output_matrix = WeightMatrix;
+end
+
+%This function will create a centroid matrix with 3 centroids
+function centroid = centroid_matrix(centroid_one, centroid_two, centroid_three)
+    centroid = [centroid_one, centroid_two, centroid_three];
 end

### 2015-04-02 paper.tex
Updated member assignments
Filled out the overview and encoding sections of the lvq network

@@
 We then constructed the Maxnet which was given the Hammingnet output as a parameter.
-It subtracts 1 from each element until a single zero value is found, declaring it the smallest hamming distance.
+It subtracts an epsilon (which we specified as the smallest element in the hamming vector) from each element until a single zero value is found, declaring it the smallest hamming distance.
 This index represents the prototype which is most similar to the input, suggesting the input must be of this classification.
@@
 Deciding how to encode our images was a bit tricky.
-We played with a few different ways of obtaining image outlines however, we decided for this network, simply finding images already in outline form would be best.
+We played with a few different ways of obtaining image outlines and decided for this network simply finding images already in outline form would be best.
 We removed inner detail from these outlines and ran them through a program we wrote.
@@
 \section{LVQ}
-
+Our LVQ network was created using the Neural Net toolkit for Matlab.
+We selected a hidden-layer size of [2 * n] to allow the target classes to be created with little room for error in the way of dying centroids based on the order of training.
+Making use of the built-in training of the toolkit, we simply constructed an input matrix consisting of all of our outlines for each group and made target vectors to use with them.
 \subsection{Image Encoding}
-The image encoding... blah blah. Type here
+Images were encoded by simply importaing the RGB map, grayscaling, and converting the grayscale 0-255 to -1 and 1 based on a threshold (taken to be 127).
+These images were also resized to the global size of 64 x 48.
+The resultant images were those that were thrown into the input matrix and used to train the lvq network.
 
@@
 \subsubsection{Project Report}
-Jonathan was tasked with the Hamming/Max section.
+Jonathan was tasked with the Hamming/Max section. He also was in charge of reporting on the Overview section.
 
@@
 
-\subsection{Skyler "Scrub on the Frub" Manzanares}
+\subsection{Skyler Manzanares}
+
 \subsubsection{Programming}
@@
 Skyler was also responsible for implementing
-the HAM network.
+the HAM network and the LVQ network.
 
@@
 William worked to create the Max layer of the Hamming/Max network and coordinate 
-inputs and outputs of the various layers, summing all components together to create a working Hamming/Max network. William was also in charge of implementing the BAM network.
-
+inputs and outputs of the various layers, summing all components together to create a working Hamming/Max network.
+William was also in charge of implementing the BAM network.
+He also was in charge of testing his BAM network creation.
 \subsubsection{Project Report}
-William was tasked to the BAM section.
+William was tasked to the BAM section and the LVQ analysis section.
 

### 2015-04-02 paper.tex

@@
 \section{LVQ}
-Our LVQ network was created using the Neural Net toolkit for Matlab.
-We selected a hidden-layer size of [2 * n] to allow the target classes to be created with little room for error in the way of dying centroids based on the order of training.
-Making use of the built-in training of the toolkit, we simply constructed an input matrix consisting of all of our outlines for each group and made target vectors to use with them.
+
 \subsection{Image Encoding}
-Images were encoded by simply importaing the RGB map, grayscaling, and converting the grayscale 0-255 to -1 and 1 based on a threshold (taken to be 127).
-These images were also resized to the global size of 64 x 48.
-The resultant images were those that were thrown into the input matrix and used to train the lvq network.
+The image encoding... blah blah. Type here
 

### 2015-04-02 TestBAM.m
Added BAM testing facilities which allow on the fly testing

@@ -1,0 +1,145 @@
+function out = TestBAM( input_args )
+    %Construct File Paths
+    DogFilePath = 'proj2out/i/dog';
+    ElepFilePath = 'proj2out/i/elep';
+    GirFilePath = 'proj2out/i/girf';
+    BiplaneFilePath = 'proj2out/ii/biplanes';
+    JetFilePath = 'proj2out/ii/jetfighters';
+    AirbusFilePath = 'proj2out/ii/passengers'
+    %Define Class Vectors
+    DogClass = [1 -1 -1 1 1 -1];
+    BiplaneClass = DogClass
+    ElepClass = [1 1 -1 -1 -1 -1];
+    JetClass = ElepClass;
+    GirClass = [1 1 1 -1 1 1];
+    AirbusClass = GirClass;
+    
+    %Define Centroid Matrices
+    DogCentroid = Weight(DogFilePath);
+    ElepCentroid = Weight(ElepFilePath);
+    GirCentroid = Weight(GirFilePath);
+    BiplaneCentroid = Weight(BiplaneFilePath);
+    JetCentroid = Weight(JetFilePath);
+    AirbusCentroid = Weight(AirbusFilePath);
+    
+    %Get File names
+    DogImages = dir('proj2out/i/dog/*jpg');
+    ElepImages = dir('proj2out/i/elep/*jpg');
+    GirImages = dir('proj2out/i/girf/*jpg');
+    BiplaneImages = dir('proj2out/ii/biplanes/*jpg');
+    JetImages = dir('proj2out/ii/jetfighters/*jpg');
+    AirbusImages = dir('proj2out/ii/passengers/*jpg');
+    %Test Dog Images
+    AnimalCentroid = centroidMatrix(DogCentroid, ElepCentroid, GirCentroid);
+    AnimalClass = classMatrix(DogClass, ElepClass, GirClass);
+    DogCorrect = 0;
+    DogIncorrect = 0;
+    for i=1:length(DogImages)
+       DogFile = getfield(DogImages(i), 'name');
+       TestVector = Weight(strcat(DogFilePath,'/',DogFile));
+       ResultVector = bam(TestVector, AnimalCentroid, AnimalClass);
+       if (isequal(ResultVector, DogClass))
+          fprintf('%s was correctly classified!\n', DogFile);
+          DogCorrect = DogCorrect + 1;
+       else
+          fprintf('%s was misclassified!\n', DogFile);
[…]

### 2015-04-02 bam.m

@@ -6,8 +6,23 @@ function output_vector = bam( input_vector, centroid_matrix, class_matrix)
     %This is the X layer of neurons
     WeightMatrix = bam_weight(class_matrix, centroid_matrix);
     %The Y Layer association:
-    Y_classification = input_vector * WeightMatrix;
-    output_vector = Y_classification;
+    
+    %fprintf('Finding Y classification Vector\n');
+    %fprintf('Input Vector Length = %d\n', length(input_vector));
+    %fprintf('Weight: C = %d, R = %d\n', wCol, wRow);
+    Y_classification = input_vector' * WeightMatrix;
+    Y_length = length(Y_classification);
+    output_vector = [Y_length];
+    for i=1:Y_length
+       %fprintf('%d, ', Y_classification(i));
+       if (Y_classification(i) > 0)
+          output_vector(i) = 1;
+       elseif (Y_classification(i) < 0)
+           output_vector(i) = -1;
+       else
+           output_vector(i) = 0;
+       end
+    end
 end
 
 %Returns the X association vector. This is done by multiplying Y or our
@@ -26,7 +41,7 @@ function output_vector = bamT( class_vector, centroid_matrix, class_matrix)
     WeightMatrix = bam_weight_T(class_matrix, centroid_matrix);
     %X_association is what BAM associates with a classification.
     X_association = class_vector * WeightMatrix;
-    output_vector = X_association.
+    output_vector = X_association;
 end
 
 %Contructs a Weight Matrix based upon an input vector and a given weight
@@ -43,11 +58,17 @@ end
 function output_matrix = bam_weight( class_matrix, centroid_matrix )
     %This function applies a Bidirectional Associative Memory
     %Algorithm
-    WeightMatrix;
-    [columns, rows] = size(centroid_matrix);
+    [classCol, classRow, d] = size(class_matrix);
+    [columns, rows, d] = size(centroid_matrix);
+    WeightMatrix = zeros(columns, classRow);
+    [weightColumns, weightRows, d] = size(WeightMatrix);
     %Find weights per matrix and find sum
-    for col=1:columns
-        tmpMatrix = centroidMatrix(:,col) * class_matrix(col,:);
+    %fprintf('Contructing Weight Matrix...\n');
+    %fprintf('Weight: C = %d, R = %d\n', weightColumns, weightRows);
+    for col=1:classCol
[…]

### 2015-04-02 HammingMax.m
redefined old hammingMax function to be a imageMatrix returning function. Created new HammingMax script

@@ -1,74 +1,3 @@
-function output=HammingMax(input)
-    
+function output=HammingMax(centroidMatrix, inputVector)
 
-    if (~isdir(input))
-        %assume its a single file name
-        fprintf('Processing file: %s\n', input);
-        img = polarize(input);
-        output = img(:);
-        output = output';
-        return;
-    else
-        olddir = pwd;
-        cd(input);
-    
-        files = dir('*.jpg');
-        
-        %init empty matrix
-        output = zeros(3072, length(files));
-        for i=1:length(files)
-            filename = files(i).name;
-            fprintf('Processing file: %s\n', filename);
-            
-            %polarize the image
-            img = polarize(filename);
-            
-             %get image as a 1 x n vector
-            vect = img(:);
-
-            %transpose so it's a column vector
-            vect = vect';
-
-            %set the i'th COL to be the same as our vector
-            output(:,i) = vect;
-            i = i + 1;
-            
-        end
-    end
-    
-    %return to the old directory
-    cd(olddir);
-
-end
-
-function output=polarize(img)
-    if (ischar(img))
-       img = getImage(img);
-    end
-    
-    img = resizeImage(img);
-    
-    output = rgb2gray(img);
-    output = threshhold(output);
-end
-
-function img=getImage(filename)
-    img = imread(filename);
-end
-
-function img=resizeImage(imgIn)
-    img=imresize(imgIn, [48, 64]);
-end
-
-function output=threshhold(InputMatrix)
-    [w,h,d] = size(InputMatrix);
-    for i=1:w
-    for j=1:h
-       if (InputMatrix(i,j) < 128)
-          output(i,j) = -1;
-       else
-           output(i,j) = 1;
-       end
-    end
-    end
 end

### 2015-04-02 HammingMax.m
Tie hamming and max network layers together. A simpel call to HammingMax now returns the centroid most like the passed input vector

@@ -1,3 +1,7 @@
 function output=HammingMax(centroidMatrix, inputVector)
-
+    hammingVect = hamming(inputVector, centroidMatrix);
+    
+    maxIndex = maxNet(hammingVect);
+    
+    output = centroidMatrix(:, maxIndex);
 end

### 2015-04-02 HammingMax.m
added comments

@@ -1,7 +1,14 @@
+%Uses hamming distance to evaluate which of the centroids in the passed
+%centroid matrix is closest the the input vector.
+%This function returns the centroid closest to the input vector.
 function output=HammingMax(centroidMatrix, inputVector)
+    %Use hamming network to get the hamming distance between each centroid
+    %and the input vector
     hammingVect = hamming(inputVector, centroidMatrix);
     
+    %Find the index of the closest centroid
     maxIndex = maxNet(hammingVect);
     
+    %set output to be the centroid that was closest
     output = centroidMatrix(:, maxIndex);
 end

### 2015-04-02 paper.tex
Began working on the Project Report (BAM)

--- 2015-04-02 paper.tex
@@
 \subsection{Image Encoding}
-The image encoding... blah blah. Type here
+All images being imported into BAM are required to be in a JPG format. These
+images are then imported, resized into a standard format, and then polarized.
+Each polarized image is then translated into a single dimensional vector.
+Each 'class' of images are grouped together column wise to create a centroid
+matrix.
 
 \subsection{Performance}
-Here is where we need to talk about how long it took and how good it was. We
-also might want to mention the size limitations this introduced!
+The Bidirectional Associative Memory implementation performed rather poorly.
+Most of the associations were directed towards a specific centroid, resulting
+in at least 1 'class' performing extremely well. The results of our
+experiment are as follows.
+Animal Results:
+    Dog:
+        7 Correctly Classified
+        3 Incorrectly Classified
+    Elephant:
+        1 Correctly Classified
+        9 Incorrectly Classified
+    Giraffe:
+        0 Correctly Classified
+        9 Correctly Classifed
+Plane Results:
+    Biplane:
+        0 Correctly Classified
+        10 Incorrectly Classified
+    Jet Results:
+        5 Correctly Classified
+        5 Incorrectly Classified
+    Airbus Results:
+        0 Correctly Classified
+        7 Incorrectly Classified
+Marine Results:
+    Ships:
+        0 Correctly Classified
+        5 Incorrectly Classified
+    Submarine Results:
+        8 Correctly Classified
+        0 Incorrectly Classified
+    Whale Results:
+        3 Correctly Classified
+        7 Incorrectly Classified
 
+It seems that the BAM implementation attempted to classify nearly all animals
+as dogs. For planes the network had more diverse attempts to classify each
+object, although incorrectly. The marine results showed the most diverse and
+correct classifications. Although it does seem that BAM attempted to describe
+everything as either a submarine or a whale.
 \subsection{Sensitivity}

### 2015-04-02 paper.tex
Began working on the Project Report (BAM)
Worked on documenting BAM in the paper

@@
 
-\subsection{Image Encoding}
+\subsection{Encoding}
+\subsubsection{Images}
 All images being imported into BAM are required to be in a JPG format. These
@@
 
+\subsubsection{Classifications}
+The classifications used by BAM were encoded as orthogoal vectors of length 6.
+Each class 'supersection' had a total of 3 classes. The animal supersection
+includes Dogs, Elephants, and Giraffes. The Plane supersection includes Biplanes,
+Jets, and Airbuses. Finally the Marine supersection includes Ships, Submarines,
+and Whales. Each supersection is treated separately. The encodings for Animals
+are used again in Planes and Marines. This was to make the classification
+encodings as simple yet distant as possible.
 \subsection{Performance}
@@
 everything as either a submarine or a whale.
+
 \subsection{Sensitivity}
-This section is about how badly noise and the size disrupted our accuracy
+Noise significantly disrupted the creation of the centroids in our Project.
+As a result we removed all excessive details and attempted to leave just
+the pure outlines. Of course this also may have made our centroid to being
+too sanitied and noisy images would be more likely to be misclassified.
 
 \subsection{Comments}
-It says "your own observation and conclusions about the experiment."
-I'm thinking we talk generally about how it did (like a conclusion) and how
-what we did ended up working.
+BAM performed rather poorly. It appeared that BAM favored a single class when
+attempting to classify. However I believe this is a result of our encoding 
+scheme. If we had made our own outlines our network could have performed 
+better. Larger sizes could also give some accuracy in exchange for computational
+power.
 
@@
 NOTHING HE DID NOTHING 0 percent FOR HIM....DAMN YOU SKYLER
-
+SKYLER, SKYYYYLLLLEERRRRR, SKYLLLLERRR NOOOOOOOOOOOOOOOOOOOOO
 \subsection{Skyler Manzanares}

### 2015-04-02 paper.tex
Update paper.tex
Filled out performance sections of the Hamming/MAX

@@
 \subsection{Image Encoding}
-The image encoding... blah blah. Type here
+the image encoding blah blah. Type here
 
@@
 \subsection{Performance}
-Here is where we need to talk about how long it took and how good it was. We
-also might want to mention the size limitations this introduced!
-
+The Hamming/MAX did an excellent job when classifying animals.
+Both the aquatic classes and the planes had classifications that were completely incorrect, and another that was completely correct.
+We attribute this half-sided success to the images we selected for testing and for centroid-generation; the animals were distinct enough that we could tell the difference between the centroids when viewing them.
+The planes were a mess of lines due to poor image selection.
+The ships had very sporatic images used to train, and the resultant centroid was a mess.
 \subsection{Sensitivity}
-This section is about how badly noise and the size disrupted our accuracy
+This network was very sensitive to noise.
+Because it was feed-forward and used hamming distance between vectors, the most important thing was literally how many pixels matched up.
+Because of this, noise was very detrimental to classification accuracy.
 
 \subsection{Comments}
-It says "your own observation and conclusions about the experiment."
-I'm thinking we talk generally about how it did (like a conclusion) and how
-what we did ended up working.
+We constructed out Hamming/MAX layer as per instructions of Lab 2.
+This led us to become extremely confused, as we weren't using a neural network but the linear-algebra equivalent.
+We didn't really use neurons.
+We just used applied linear algebra.
+Regardless, we went forward with the matrix-only implementation and were pretty pleased with the results.
+
+By far the Hamming/Max was easiest for us to break down and implement.
 

### 2015-04-02 paper.tex
Discussed noise and comments of lvq

@@
 \subsection{Performance}
-Here is where we need to talk about how long it took and how good it was. We
-also might want to mention the size limitations this introduced!
+Our LVQ had some pretty good performance but also some poor performance.
+When testing animals against eachother (dogs, elephants, and giraffes) the network maintained a fairly consistent classification.
+40
 
 \subsection{Sensitivity}
-This section is about how badly noise and the size disrupted our accuracy
+Being a feed-back network, the LVQ did fairly well to adapt to small amounts of noise.
+Because the centroids themselves had noise, the LVQ did the best overall out of all implementations.
+Being able to try over and over to get the actual centroid from a distorted image really helped aleviate a lot of the problems that came with the noise.
 
 \subsection{Comments}
-It says "your own observation and conclusions about the experiment."
-I'm thinking we talk generally about how it did (like a conclusion) and how
-what we did ended up working.
+Because we used the neural net toolkit, constructing the lvq required the most work.
+This seems paradoxical, but the lack of easy-to-locate documentation on the neural net toolkit and the functions it provides set us back quite a ways.
 

### 2015-04-02 paper.tex
Filled out sensitivity section of HAM

@@
 \subsection{Sensitivity}
-This section is about how badly noise and the size disrupted our accuracy
+The hopfield was incredibly resilient to noise.
+This was most likely due to the fact that it was a feed-back network, so noise was able to be gradually phased out.
+Because our method of creating centroids created noise in the centroids, the hopfield did pretty good in regards to eliminating the noise.
+
+When deciding on values for delta, we originally imagined a value of about .1 would be best.
+Upon testing, we found very quickly that much smaller delta values worked better, as the HAM was converging very quickly.
 

### 2015-04-02 paper.tex
Update paper.tex

--- 2015-04-02 paper.tex
@@
 \subsection{Performance}
-Here is where we need to talk about how long it took and how good it was. We
-also might want to mention the size limitations this introduced!
+Our LVQ had some pretty good performance but also some poor performance.
+When testing animals against eachother (dogs, elephants, and giraffes) the network maintained a fairly consistent classification.
+It returned 21\% false negatives by misclassifying 4 dogs and 2 elephants, all as giraffes.
+However the other 79\% of animals were correctly classified.
+Aircraft were a little trickier.
+With 66\% overall correct classification, most aircraft were classified as Jetfighters.
+All ten jet fighters were correctly classified and 9 passenger aircraft and biplanes misclassified.
+Sea-fareing objects were not as great.
+Not a single image was classified as a ship.
+However, 70\% of whales were correctly classified and all of the submarines were correctly classified.
+\begin{itemize}
+\end{itemize}
 

### 2015-04-02 paper.tex

--- 2015-04-02 paper.tex
@@
 When testing animals against eachother (dogs, elephants, and giraffes) the network maintained a fairly consistent classification.
-40
+It returned 21\% false negatives by misclassifying 4 dogs and 2 elephants, all as giraffes.
+However the other 79\% of animals were correctly classified.
+Aircraft were a little trickier.
+With 66\% overall correct classification, most aircraft were classified as Jetfighters.
+All ten jet fighters were correctly classified and 9 passenger aircraft and biplanes misclassified.
+Sea-fareing objects were not as great.
+Not a single image was classified as a ship.
+However, 70\% of whales were correctly classified and all of the submarines were correctly classified.
+\begin{itemize}
+\end{itemize}
 

### 2015-04-02 paper.tex
Oh no theres a merge error on the paper

--- 2015-04-02 paper.tex
@@
 \subsection{Image Encoding}
-the image encoding blah blah. Type here
+The image encoding... blah blah. Type here
 
@@
 \subsection{Performance}
-The Hamming/MAX did an excellent job when classifying animals.
-Both the aquatic classes and the planes had classifications that were completely incorrect, and another that was completely correct.
-We attribute this half-sided success to the images we selected for testing and for centroid-generation; the animals were distinct enough that we could tell the difference between the centroids when viewing them.
-The planes were a mess of lines due to poor image selection.
-The ships had very sporatic images used to train, and the resultant centroid was a mess.
+Here is where we need to talk about how long it took and how good it was. We
+also might want to mention the size limitations this introduced!
+
 \subsection{Sensitivity}
-This network was very sensitive to noise.
-Because it was feed-forward and used hamming distance between vectors, the most important thing was literally how many pixels matched up.
-Because of this, noise was very detrimental to classification accuracy.
+This section is about how badly noise and the size disrupted our accuracy
 
 \subsection{Comments}
-We constructed out Hamming/MAX layer as per instructions of Lab 2.
-This led us to become extremely confused, as we weren't using a neural network but the linear-algebra equivalent.
-We didn't really use neurons.
-We just used applied linear algebra.
-Regardless, we went forward with the matrix-only implementation and were pretty pleased with the results.
-
-By far the Hamming/Max was easiest for us to break down and implement.
+It says "your own observation and conclusions about the experiment."
+I'm thinking we talk generally about how it did (like a conclusion) and how
+what we did ended up working.
 
@@
 encodings as simple yet distant as possible.
+
 \subsection{Performance}
@@
 
+These errors are likely due to bad encoding. Our group noticed that large
+images with thin outlines lost information when being resized to a smaller 
+image. Also most of our outlines were collected from the internet. These
+outlines were incredibly diverse and perhaps the details of each image were
+simply 'drowned' out in the diversity of the images. If we standardized our 
+input we would have likely seen better results.
+
 \subsection{Sensitivity}
@@
 \subsection{Performance}
-Our LVQ had some pretty good performance but also some poor performance.
-When testing animals against eachother (dogs, elephants, and giraffes) the network maintained a fairly consistent classification.
-It returned 21\% false negatives by misclassifying 4 dogs and 2 elephants, all as giraffes.
-However the other 79\% of animals were correctly classified.
-Aircraft were a little trickier.
-With 66\% overall correct classification, most aircraft were classified as Jetfighters.
-All ten jet fighters were correctly classified and 9 passenger aircraft and biplanes misclassified.
-Sea-fareing objects were not as great.
-Not a single image was classified as a ship.
-However, 70\% of whales were correctly classified and all of the submarines were correctly classified.
-\begin{itemize}
-\end{itemize}
+Here is where we need to talk about how long it took and how good it was. We
+also might want to mention the size limitations this introduced!
 

### 2015-04-02 TestBAM.m

@@ -51,175 +51,192 @@ function out = TestBAM( input_args )
     %Test Dog Images
     AnimalCentroid = centroidMatrix(DogCentroid, ElepCentroid, GirCentroid);
     AnimalClass = classMatrix(DogClass, ElepClass, GirClass);
-    DogCorrect = 0;
-    DogIncorrect = 0;
+    Dogs_Dog = 0;
+    Elephants_Dog = 0;
+    Giraffes_Dog = 0;
     for i=1:length(DogImages)
        DogFile = getfield(DogImages(i), 'name');
        TestVector = Weight(strcat(DogFilePath,'/',DogFile));
        ResultVector = bam(TestVector, AnimalCentroid, AnimalClass);
        if (isequal(ResultVector, DogClass))
-          fprintf('%s was correctly classified!\n', DogFile);
-          DogCorrect = DogCorrect + 1;
-       else
-          fprintf('%s was misclassified!\n', DogFile);
-          DogIncorrect = DogIncorrect + 1;
-       end
+          Dogs_Dog = Dogs_Dog + 1;
+       elseif (isequal(ResultVector, ElepClass))
+           Elephants_Dog = Elephants_Dog + 1;
+       elseif (isequal(ResultVector, GirClass))
+           Giraffes_Dog = Giraffes_Dog + 1;
     end
     %Test Elephant Images
-    ElepCorrect = 0;
-    ElepIncorrect = 0;
+    Dogs_Elephant = 0;
+    Elephants_Elephant = 0;
+    Giraffes_Elephant = 0;
     for i=1:length(ElepImages)
        ElepFile = getfield(ElepImages(i), 'name');
        TestVector = Weight(strcat(ElepFilePath,'/',ElepFile));
        ResultVector = bam(TestVector, AnimalCentroid, AnimalClass);
-       if (isequal(ResultVector, ElepClass))
-          fprintf('%s was correctly classified!\n', ElepFile);
-          ElepCorrect = ElepCorrect + 1;
-       else
-          fprintf('%s was misclassified!\n', ElepFile);
-          ElepIncorrect = ElepIncorrect + 1;
+       if (isequal(ResultVector, DogClass))
+          Dogs_Elephant = Dogs_Elephant + 1;
+       elseif (isequal(ResultVector, ElepClass))
[…]

### 2015-04-02 paper.tex

--- 2015-04-02 paper.tex
@@
 everything as either a submarine or a whale.
+
+These errors are likely due to bad encoding. Our group noticed that large
+images with thin outlines lost information when being resized to a smaller 
+image. Also most of our outlines were collected from the internet. These
+outlines were incredibly diverse and perhaps the details of each image were
+simply 'drowned' out in the diversity of the images. If we standardized our 
+input we would have likely seen better results.
 

### 2015-04-02 paper.tex
Updated presentation assignments

--- 2015-04-02 paper.tex
@@
 \subsubsection{Project Presentation}
-NOTHING HE DID NOTHING 0 percent FOR HIM....DAMN YOU SKYLER
-SKYLER, SKYYYYLLLLEERRRRR, SKYLLLLERRR NOOOOOOOOOOOOOOOOOOOOO
+Jonathan updated the project with accurate testing results
+
 \subsection{Skyler Manzanares}
@@
 \subsubsection{Project Presentation}
-lulz he ain't done a thing.  0\% for you
+Skyler laid out the outline of the slides and filled in the description of all the neural networks. He also wrote the encoding section.
 
@@
 \subsubsection{Project Presentation}
-nuthin. no soup for you
+William's main contribution to the presentation was results.
 

### 2015-04-02 paper.tex
Added content to the HAM network

@@
 \section{Hopfield Autoassociative Memory Network}
-Our hopfield network was terrific! Type stuff here
+The HAM network we constructed worked by creating large symmetric weight-matrices from image centroids (see Image Encoding subsection) to classify input vectors.
+The network is feed-back, meaning it feeds the resultant output vector back into itself as input until the network no longer exhibits any change on the vector.
+
+We noticed that our HAM, while moving the input vector much closer to the proper centroid vector, was not able to make concrete classifications.
+Because this is the realm of soft computing, we decided the return the classificaton that was closest to the convergent vector.
+To decide which centroid was closest, we actually plugged the final resultant vector from the HAM into our Hamming/MAX network.
+This allowed us to make the short jump to the nearest centroid.
 
 \subsection{Image Encoding}
-the image encoding blah blah. Type here
+Images were first converted from rgb to grayscale, and then run through a threshold function to polarize the images.
+These images were then fed into a function that took the average of each pixel value across all input images and returned the resulting centroid.
+
+This same encoding and centroid-generating technique was used in all other networks except the LVQ with only slight modifications.
+
+Images, when being polarized, were scaled down to a universal size of 64 x 48. This meant our centroids were also 64 x 48 matrices as well.
 
@@
 \subsection{Comments}
-It says "your own observation and conclusions about the experiment."
-I'm thinking we talk generally about how it did (like a conclusion) and how
-what we did ended up working.
+Surprisingly the HAM was the second easiest networks to implement.
+We found that the implementation of it ended up being suprisingly intuitive.
+Even though we were using large matrices, the 'training' time (creation of weight matrix) was incredibly small (small enough we didn't record it) and classification times were even faster.
 

### 2015-04-02 paper.tex
Update paper.tex

--- 2015-04-02 paper.tex
@@
 encodings as simple yet distant as possible.
-
 \subsection{Performance}
@@
 
-These errors are likely due to bad encoding. Our group noticed that large
-images with thin outlines lost information when being resized to a smaller 
-image. Also most of our outlines were collected from the internet. These
-outlines were incredibly diverse and perhaps the details of each image were
-simply 'drowned' out in the diversity of the images. If we standardized our 
-input we would have likely seen better results.
-
 \subsection{Sensitivity}
@@
 However, 70\% of whales were correctly classified and all of the submarines were correctly classified.
+Animal Results:
 \begin{itemize}
+    \item Dog:
+    \begin{itemize}
+        \item 6 Correctly Classified
+        \item 4 Incorrectly Classified
         \end{itemize}
-
+    \item Elephant:
+    \begin{itemize}
+        \item 8 Correctly Classified
+        \item 2 Incorrectly Classified
+        \end{itemize}
+   \item Giraffe:
+   \begin{itemize}
+        \item 9 Correctly Classified
+        \item 0 Correctly Classifed
+        \end{itemize}
+\end{itemize}
+Plane Results:
+\begin{itemize}
+    \item Biplane:
+    \begin{itemize}
+        \item 7 Correctly Classified
+        \item 3 Incorrectly Classified
+        \end{itemize}
+    \item Jet Results:
+    \begin{itemize}
+        \item 10 Correctly Classified
+        \item 0 Incorrectly Classified
+        \end{itemize}
+    \item Passenger Results:
+    \begin{itemize}
+        \item 1 Correctly Classified
+        \item 6 Incorrectly Classified
+        \end{itemize}
+\end{itemize}
+Marine Results:
+\begin{itemize}
+    \item Ships:
+    \begin{itemize}
+        \item 0 Correctly Classified
+        \item 5 Incorrectly Classified
+        \end{itemize}
+    \item Submarine Results:
+    \begin{itemize}
+        \item 8 Correctly Classified
+        \item 0 Incorrectly Classified
+        \end{itemize}
+    \item Whale Results:
+    \begin{itemize}
+        \item 7 Correctly Classified
+        \item 3 Incorrectly Classified
+        \end{itemize}
+\end{itemize}        
 \subsection{Sensitivity}

### 2015-04-02 paper.tex
Update paper.tex

--- 2015-04-02 paper.tex
@@
 \subsection{Performance}
-Here is where we need to talk about how long it took and how good it was. We
-also might want to mention the size limitations this introduced!
+The HAM network worked very well for classifying Animals and sea-craft, but rather poorly for airplanes.
+80\% of dogs were classified correctly along with every giraffe and all but one elephant.
+All submarines and all ships were also classified correctly, however, whales were pretty evenly classified as either a whale, submarine, or ship.
+Airplanes however were not handled well at all.
+Likely due to ambiguity in passenger airline encoding, all but one airplane image was classified as a passenger plane.
+While this means that all passenger planes were correctly classified, no jet fighters were correct.
+Nine of the ten biplanes were also classified as passenger craft, however the one shining nugget was the remaining biplane which was correctly classified as such.
+It must have really looked like a biplane as it was the only aircraft that wasn't classified as a passenger airline.
+
+Animal Results:
+\begin{itemize}
+    \item Dog:
+    \begin{itemize}
+        \item 8 Correctly Classified
+        \item 2 Incorrectly Classified
+        \end{itemize}
+    \item Elephant:
+    \begin{itemize}
+        \item 9 Correctly Classified
+        \item 1 Incorrectly Classified
+        \end{itemize}
+   \item Giraffe:
+   \begin{itemize}
+        \item 9 Correctly Classified
+        \item 0 Correctly Classifed
+        \end{itemize}
+\end{itemize}
+Plane Results:
+\begin{itemize}
+    \item Biplane:
+    \begin{itemize}
+        \item 1 Correctly Classified
+        \item 9 Incorrectly Classified
+        \end{itemize}
+    \item Jet Results:
+    \begin{itemize}
+        \item 0 Correctly Classified
+        \item 10 Incorrectly Classified
+        \end{itemize}
+    \item Passenger Results:
+    \begin{itemize}
+        \item 7 Correctly Classified
+        \item 0 Incorrectly Classified
+        \end{itemize}
+\end{itemize}
+Marine Results:
+\begin{itemize}
+    \item Ships:
+    \begin{itemize}
+        \item 5 Correctly Classified
+        \item 0 Incorrectly Classified
+        \end{itemize}
+    \item Submarine Results:
+    \begin{itemize}
+        \item 8 Correctly Classified
+        \item 0 Incorrectly Classified
+        \end{itemize}
+    \item Whale Results:
+    \begin{itemize}
+        \item 3 Correctly Classified
+        \item 7 Incorrectly Classified
+        \end{itemize}
+\end{itemize}
 

### 2015-04-02 paper.tex
Update paper.tex
Merrggiinnnngggggggg

@@
 experiment are as follows.
-Animal Results:
-    Dog:
-        7 Correctly Classified
-        3 Incorrectly Classified
-    Elephant:
-        1 Correctly Classified
-        9 Incorrectly Classified
-    Giraffe:
-        0 Correctly Classified
-        9 Correctly Classifed
-Plane Results:
-    Biplane:
-        0 Correctly Classified
-        10 Incorrectly Classified
-    Jet Results:
-        5 Correctly Classified
-        5 Incorrectly Classified
-    Airbus Results:
-        0 Correctly Classified
-        7 Incorrectly Classified
-Marine Results:
-    Ships:
-        0 Correctly Classified
-        5 Incorrectly Classified
-    Submarine Results:
-        8 Correctly Classified
-        0 Incorrectly Classified
-    Whale Results:
-        3 Correctly Classified
-        7 Incorrectly Classified
 
-It seems that the BAM implementation attempted to classify nearly all animals
-as dogs. For planes the network had more diverse attempts to classify each
-object, although incorrectly. The marine results showed the most diverse and
-correct classifications. Although it does seem that BAM attempted to describe
-everything as either a submarine or a whale.
+\begin{itemize}
+    \item Animals
+        \begin{itemize}
+            \item Dog Results:
+                \begin{itemize}
+                    \item Classified as Dog:........7
+                    \item Classified as Elephant:...0
+                    \item Classified as Giraffe:....2
+                    \item Classified as Unknown:....1
+                \end{itemize}
+            \item Elephant Results:
+                \begin{itemize}
+                    \item Classified as Dog:........0
+                    \item Classified as Elephant:...1
+                    \item Classified as Giraffe:....1
+                    \item Classified as Unknown.....8
+                \end{itemize}
+            \item Giraffe Results:
+                \begin{itemize}
+                    \item Classified as Dog:........0
+                    \item Classified as Elephant:...0
+                    \item Classified as Giraffe:....9
+                    \item Classified as Unknown:....0
+                \end{itemize}
+        \end{itemize}
+    \item Planes
+        \begin{itemize}
+            \item Biplane Results:
+                \begin{itemize}
+                    \item Classified as Biplane:....0
+                    \item Classified as Jet:........3
+                    \item Classified as Airbus:.....0
+                    \item Classified as Unknown:....7
+                \end{itemize}
+            \item Jet Results:
+                \begin{itemize}
+                    \item Classified as Biplane:....0
+                    \item Classified as Jet:........5
+                    \item Classified as Airbus:.....0
+                    \item Classified as Unknown:....5
+                \end{itemize}
+            \item Airbus Results:
+                \begin{itemize}
+                    \item Classified as Biplane:....0
+                    \item Classified as Jet:........4
+                    \item Classified as Airbus:.....0
+                    \item Classified as Unknown:....3
+                \end{itemize}
+        \end{itemize}
+    \item Marines
+        \begin{itemize}
+            \item Ship Results:
+                \begin{itemize}
+                    \item Classified as Ship:.......0
+                    \item Classified as Submarine:..0
+                    \item Classified as Whale:......0
+                    \item Classified as Unknown:....5
+                \end{itemize}
+            \item Submarine Results:
+                \begin{itemize}
+                    \item Classified as Ship:.......0
+                    \item Classified as Submarine:..8
+                    \item Classified as Whale:......0
+                    \item Classified as Unknown:....0
+                \end{itemize}
+            \item Whale Results:
+                \begin{itemize}
+                    \item Classified as Ship:.......0
+                    \item Classified as Submarine:..5
+                    \item Classified as Whale:......3
+                    \item Classified as Unknown:....2
+                \end{itemize}
+        \end{itemize}
+\end{itemize}
+
+While often the BAM misclassified objects, most of the time it told us that
+it could not classify it. Our BAM implementation could not classify Elephants, 
+Biplanes, and Ships but it could tell us that of the inputs used, it could not
+classify them. Otherwise the network performed extremely well with objects
+such as dogs and submarines.
+
+Of the occasions that the BAM network misclassified, such as the airbus, this is 
+likely due to a poorly defined centroid. If we had improved our encoding perhaps 
+we could have gotten some better results.
 
@@
 \subsection{Comments}
-BAM performed rather poorly. It appeared that BAM favored a single class when
+BAM performed rather poorly overall. It appeared that BAM favored a single class when 
 attempting to classify. However I believe this is a result of our encoding 
@@
 Hamming/Max network and the creation of centroids for the networks based on a
-large number of sample inputs. He was completely responsible for creating the Hamming layer of the Hamming/MAX network, and worked in conjunction with the rest of the team when creating the centroids.
+large number of sample inputs.
+He was completely responsible for creating the Hamming layer of the Hamming/MAX network, and worked in conjunction with the rest of the team when creating the centroids.
+He was responsible for testing the HAM and LVQ networks in whole and gathering the results.
 
 \subsubsection{Project Report}
-Jonathan was tasked with the Hamming/Max section. He also was in charge of reporting on the Overview section.
+Jonathan was tasked with the Hamming/Max section. He also was in charge of reporting on the LVQ section and filling in result data.
 
 \subsubsection{Project Presentation}
-Jonathan updated the project with accurate testing results
+Jonathan updated the project with accurate testing results.
 

### 2015-04-02 paper.tex
Update paper.tex
Cant even
Wooordd

woorrdsss

@@
 \section{Overview}
-
+This paper evaluates our results on various Neural Networks. These Neural
+Networks were tested on standardized inputs and attempted to classify each
+input appropriately. The performance of each Neural Network is determined by
+the validity of their classifications. Each evaluation is discussed in more
+detail in their appropriate sections.
 \section{Hopfield Autoassociative Memory Network}
